Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-29 wearables_survey.tex
done with methodology section

\subsection{Risk and Benefit Assessment}
The next set of questions are with respect to the Fischoff study on users’ perception of benefit and risk. We wanted to study personal but also broad perceptions of wearble risks. the We prompted the users with the same prompt that the participants in the Fischoff study was presented with, giving instructions to consider gross risk and gross benefits for a long period of time for all people, with specific instructions to numerical rankings. We did this so that we can calibrate the new technologies that we ask about with the existing seminal study. Prompt can be seen at appendix \ref{sec:prompt}.

After that prompt, users were given this question and asked to fill in the numbers according to the previous prompt’s instructions. Each person got the same four calibration questions (handguns, motorcycles, lawnmowers, electricity), and 1/20 randomized new technology.  People rated the same randomized new technology for both benefit and risk.

\textit{Fill in your benefit numbers for the following technologies:}\\
\textit{Fill in your risk numbers for the following technologies:}

\textit{Handguns}: \_\_\_\_\_\_\_ \\
\textit{Motorcycles}: \_\_\_\_\_\_\_\\
\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
\textit{<New Tech Here>}: \_\_\_\_\_\_\_\\
\textit{Electricity}: \_\_\_\_\_\_\_\\

The list of technologies included: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice based emotion detection, location tracking, speech to text, language detection, heart rate detection, age detection, and gender detection.

>>>>

\subsection{Risk and Benefit Assessment}
In addition to investigating personal reactions to particular scenarios, we also wanted to study broad perceptions of various new technologies. Each participant saw 1 risk assessment question and 1 benefit assessment question regarding the same four previously studied technologies from the the seminal risk perception study by Fischhoff (handguns, motorcycles, lawnmowers, electricity), and 1 of the 20 new technologies.  Participants were asked to rate the same randomized new technology for both risk and benefit assessment. The format of the questions were as follows:

\textit{Fill in your risk (benefit) numbers for the following technologies:}\\[-.5cm]

\textit{Handguns}: \_\_\_\_\_\_\_ \\
\textit{Motorcycles}: \_\_\_\_\_\_\_\\
\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
\textit{<Randomized>}: \_\_\_\_\_\_\_\\
\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]

To parallel the risk perception study, we gave our participants a similar prompt which instructed the participants to numerically express the conceived gross risk (gross benefit) for a long period of time for all parties involved. The prompt can be seen at appendix \ref{sec:prompt}. Specifically, we asked participants to evaluate the of following 20 new technologies: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice based emotion detection, location tracking, speech to text, language detection, heart rate detection, age detection, and gender detection.
